full title

### 2020-11-21 paper/pldi21/intro.tex
Added figure 8. Removed inred in intro and motivation.

\begin{figure}[t]
  \centering
  \includegraphics[width=\linewidth]{img/performance_v8v7}
  \vspace*{-2em}
  \caption{Performance of a dynamic analyzer and a static analyzer for V8
  benchmarks version 7}
  \label{fig:performance}
  \vspace*{-1em}
\end{figure}

To alleviate these problems, researchers have leveraged
dynamic analysis during static analysis.  Because dynamic
analyzers such as Jalangi~\cite{jalangi} and DLint~\cite{dlint} run on
highly-optimized commercial JavaScript engines, they are much faster than
static analyzers.  Figure~\ref{fig:performance} shows that the dynamic analyzer
Jalangi is \inred{X.X}x faster than the static analyzer SAFE for V8 benchmarks
version 7.  Using high performance dynamic analysis, researchers have
reduced the scope of static analysis~\cite{determinacy, blendedJS} and constructed
initial abstract states~\cite{battles, eha} and automatic modeling of opaque
code~\cite{sra}.

@@

In this paper, we propose a novel technique to fully utilize
the high performance of dynamic analysis for JavaScript static
analysis in a sound manner by using \textit{dynamic shortcuts}.
During static analysis, one can take a dynamic shortcut, which
consists of three parts: 1) converting the current abstract state to
its corresponding \textit{sealed symbolic state}, 2) performing
\textit{sealed symbolic execution} on the sealed symbolic state, and
3) converting the result of the sealed symbolic execution to its
corresponding abstract state.  Our key observation is that we can use
the fast concrete execution for specific program parts while
preserving the soundness if they do not use abstract values.
For example, consider static analysis of the following code:
\begin{lstlisting}[style=myJSstyle,numbers=none]
    var v = ... // an abstract value
    var obj = { p1: v }, y = "p";
    x = obj[y + 1];
\end{lstlisting}
Because \jscode{y + 1} evaluates to \jscode{"p1"},
the third line assigns the abstract value of \jscode{v} stored in
\jscode{obj.p1} to the variable \jscode{x}.
Note that even though \jscode{obj} contains an abstract value \jscode{v},
because the third line does not ``use'' the value of \jscode{v},
we can concretely execute the code.  Based on this observation,
we introduce sealed symbolic execution, which is concrete execution
using \textit{sealed symbolic values}.  A sealed symbolic value is a
representation of an abstract value in symbolic execution; it signals
the end of the current dynamic shortcut when the sealed symbolic
execution tries to access its value.
To evaluate our technique, we implemented $\tool$ using both SAFE
and Jalangi and analyzed \inred{77} official tests of Lodash 4 library.

The contributions of this paper include the following:
\begin{itemize}
\item We present a novel technique for JavaScript static
analysis to leverage the high performance of dynamic analysis using
dynamic shortcuts.  We formally define the technique and prove
its soundness and termination.
\item We actualize the proposed technique in $\tool$, an
extended combination of SAFE and Jalangi.
\item For empirical evaluation, we analyzed \inred{77} official tests of
\inred{Lodash 4} library.  The experiment shows that $\tool$ outperforms
SAFE \inred{X.X}x on average.  Moreover, by using dynamic shortcuts
instead of manual modeling for \inred{XX.X} opaque functions,
$\tool$ improves \inred{XX.XX}\% of the analysis precision on average.
\end{itemize}

>>>>

\begin{figure}[t]
  \centering
  \includegraphics[width=\linewidth]{img/performance_v8v7}
  \vspace*{-2em}
  \caption{Performance of a dynamic analyzer and a static analyzer for a subset
  of the SunSpider benchmark}
  \label{fig:performance}
  \vspace*{-1em}
\end{figure}

To alleviate these problems, researchers have leveraged
dynamic analysis during static analysis.  Because dynamic
analyzers such as Jalangi~\cite{jalangi} and DLint~\cite{dlint} run on
highly-optimized commercial JavaScript engines, they are much faster than
static analyzers.  Figure~\ref{fig:performance} shows that the dynamic analyzer
Jalangi is 34.8x faster than the static analyzer SAFE for a subset of the
SunSpider benchmark.  Using high performance dynamic analysis, researchers have
reduced the scope of static analysis~\cite{determinacy, blendedJS} and constructed
initial abstract states~\cite{battles, eha} and automatic modeling of opaque
code~\cite{sra}.

@@

In this paper, we propose a novel technique to fully utilize
the high performance of dynamic analysis for JavaScript static
analysis in a sound manner by using \textit{dynamic shortcuts}.
During static analysis, one can take a dynamic shortcut, which
consists of three parts: 1) converting the current abstract state to
its corresponding \textit{sealed symbolic state}, 2) performing
\textit{sealed symbolic execution} on the sealed symbolic state, and
3) converting the result of the sealed symbolic execution to its
corresponding abstract state.  Our key observation is that we can use
the fast concrete execution for specific program parts while
preserving the soundness if they do not use abstract values.
For example, consider static analysis of the following code:
\begin{lstlisting}[style=myJSstyle,numbers=none]
    var v = ... // an abstract value
    var obj = { p1: v }, y = "p";
    x = obj[y + 1];
\end{lstlisting}
Because \jscode{y + 1} evaluates to \jscode{"p1"},
the third line assigns the abstract value of \jscode{v} stored in
\jscode{obj.p1} to the variable \jscode{x}.
Note that even though \jscode{obj} contains an abstract value \jscode{v},
because the third line does not ``use'' the value of \jscode{v},
we can concretely execute the code.  Based on this observation,
we introduce sealed symbolic execution, which is concrete execution
using \textit{sealed symbolic values}.  A sealed symbolic value is a
representation of an abstract value in symbolic execution; it signals
the end of the current dynamic shortcut when the sealed symbolic
execution tries to access its value.
To evaluate our technique, we implemented $\tool$ using both SAFE
and Jalangi and analyzed 269 official tests of Lodash 4 library.

The contributions of this paper include the following:
\begin{itemize}
\item We present a novel technique for JavaScript static
analysis to leverage the high performance of dynamic analysis using
dynamic shortcuts.  We formally define the technique and prove
its soundness and termination.
\item We actualize the proposed technique in $\tool$, an
extended combination of SAFE and Jalangi.
\item For empirical evaluation, we analyzed 269 official tests of
Lodash 4 library.  The experiment shows that $\tool$ outperforms
SAFE \inred{X.X}x on average.  Moreover, by using dynamic shortcuts
instead of manual modeling for \inred{XX.X} opaque functions,
$\tool$ improves the analysis precision to detect 5.97 more dead branches on
average.
\end{itemize}

### 2020-11-21 paper/pldi21/motivation.tex
Added figure 8. Removed inred in intro and motivation.

Figure~\ref{fig:example}(a) shows the \jscode{concat} function defined
in Lodash library~\cite{lodash} (v4.17.20); it is
the most popular npm package\footnote{https://www.npmjs.com/browse/depended}
and \inred{124,562} npm packages have a dependency on it.
The \jscode{concat} function creates a new array concatenating given arrays or values.
It first checks the length of \jscode{arguments} on lines 1--3.
Then, it stores the first argument to \jscode{array} on line 4 and
copies the remaining arguments to \jscode{args} on lines 5--8.
On line 9, it checks whether \jscode{array} is an array object using
the built-in function \jscode{isArray}.  If so, it creates a new array
by copying the given array via \jscode{copyArray}; otherwise,
it creates a singleton array \jscode{[array]}.  Finally, it flattens
\jscode{args} via \jscode{baseFlatten} and pushes the result to the
new array on line 11.

>>>>

Figure~\ref{fig:example}(a) shows the \jscode{concat} function defined
in Lodash library~\cite{lodash} (v4.17.20); it is
the most popular npm package\footnote{https://www.npmjs.com/browse/depended}
and 124,287 npm packages have a dependency on it.
The \jscode{concat} function creates a new array concatenating given arrays or values.
It first checks the length of \jscode{arguments} on lines 1--3.
Then, it stores the first argument to \jscode{array} on line 4 and
copies the remaining arguments to \jscode{args} on lines 5--8.
On line 9, it checks whether \jscode{array} is an array object using
the built-in function \jscode{isArray}.  If so, it creates a new array
by copying the given array via \jscode{copyArray}; otherwise,
it creates a singleton array \jscode{[array]}.  Finally, it flattens
\jscode{args} via \jscode{baseFlatten} and pushes the result to the
new array on line 11.
